### 2019-09-20 bp_intro_v3.tex
removed references to CI data

At the same time, these 
challenges that contribute to stress levels can make it hard for knowledge workers to stay focused, impact interaction with their digital environment,degrade the quality of work performed and hinder productivity.
For instance, the continuous disruptions that knowledge workers face in office work environments can lead to a higher error rate and lower 
performance~\cite{bailey2001effects,mark2008cost}.

@@

Our work builds upon previous work and extends it by performing an eight-week 
study in the workplace with 14 knowledge workers, collecting biometric and 
computer interaction data as well as experience samples on focus, awakeness, 
and stress. Our participants, who perform various job functions for a research 
and development group within a single large corporation, wore a single 
biometric armband sensor\footnote{Biovotion Everion sensor~\cite{everion}} 
with low invasiveness that captured heart-, respiration- and skin-related measures. This 
modality was chosen to ease longitudinal deployment in the field. Using 
machine learning, we created classifiers and analyzed their ability to predict 
the three productivity-related human aspects. Similarly, we captured computer 
interaction features from participants' everyday computer usage and
analyzed how a model trained using the combination
of these two training sets compares to the performance of models using each
set individually.

The results of our analysis show that biometric signals collected from a single minimally invasive sensor can be used to predict stress and its related aspects accurately, with the abstract concept of focus (predictably) being the hardest to detect. The results also show that knowledge workers' self-reported levels of stress, focus and awakeness and their physiological manifestation and prediction can vary a lot between individuals. Our results further show that overall combining biometric features with computer interaction information 
results in an improvement
over each of the training sets individually.
The main contributions of our work are:
\begin{itemize}
	\item An qualitative examination of how knowledge worker stress presents and fluctuates in the wild.
	\item The creation and analysis of measures for the automatic monitoring of knowledge workers' awakeness, stress, and focus in the workplace based on an eight-week field study with 14 office workers.
	%\item A thorough analysis of ways to increase performance, including the training sample size, time window to collect data, and the inclusion of computer interaction features.
	\item A discussion on the impact of applying this research to improve
the interaction of knowledge workers with their digital environment leading to an improvement in their productivity and well-being, besides a reflection on aspects that can be further improved in future studies.
    \end{itemize}

>>>>

At the same time, these 
challenges that contribute to stress levels can make it hard for knowledge workers to stay focused, impact interaction with their digital environment, degrade the quality of work performed and hinder productivity.
For instance, the continuous disruptions that knowledge workers face in office work environments can lead to a higher error rate and lower 
performance~\cite{bailey2001effects,mark2008cost}.

@@

Our work builds upon previous work and extends it by performing an eight-week 
study in the workplace with 14 knowledge workers, collecting biometric and 
computer interaction data as well as experience samples on focus, awakeness, 
and stress. Our participants, who perform various job functions for a research 
and development group within a single large corporation, wore a single 
biometric armband sensor\footnote{Biovotion Everion sensor~\cite{everion}} 
with low invasiveness that captured heart-, respiration- and skin-related measures. This 
modality was chosen to ease longitudinal deployment in the field. Using 
machine learning, we created classifiers and analyzed their ability to predict stress, focus, and awakeness levels.
%Similarly, we captured computer 
%interaction features from participants' everyday computer usage and
%analyzed how a model trained using the combination
%of these two training sets compares to the performance of models using each
%set individually.

In our analysis we identify several trends in day-to-day stress levels that emerged over the course of our eight-week study.
The results of our analysis also show that biometric signals collected from a single minimally invasive sensor can be used to predict stress and its related aspects accurately, with the abstract concept of focus (predictably) being the hardest to detect. Our results further show that knowledge workers' self-reported levels of stress, focus and awakeness and their physiological manifestation and prediction can vary a lot between individuals. 
%Our results further show that overall combining biometric features with computer interaction information 
%results in an improvement
%over each of the training sets individually.
The main contributions of our work are:
\begin{itemize}
	\item An qualitative examination of how knowledge worker stress presents and fluctuates in the wild.
	\item The creation and analysis of measures for the automatic monitoring of knowledge workers' awakeness, stress, and focus in the workplace based on an eight-week field study with 14 office workers.
	%\item A thorough analysis of ways to increase performance, including the training sample size, time window to collect data, and the inclusion of computer interaction features.
	\item A discussion on the impact of applying this research to improve
the interaction of knowledge workers with their digital environment leading to an improvement in their productivity and well-being, besides a reflection on aspects that can be further improved in future studies.
    \end{itemize}
